HPC--101\\Onboarding

### 2016-01-22 hpc_101/paper.tex
corrected slurm expanded

\begin{frame}
	\frametitle{What is a Job Scheduler?}
	Basic features expected of a job scheduler include:
	\begin{itemize}\footnotesize
        \item The capability to control and prioritize the execution order of unrelated jobs
        \item Allocate exclusive and/or non-exclusive access to resources to users for some duration of time so they can perform work
	\item Provides a framework for starting, executing, and monitoring work on the set of allocated resources
	\item Arbitrate contention for resources by managing a queue of pending work
	\end{itemize}
	\bigskip
	For the {\craycs}, we utilize the \textbf{S}imple \textbf{L}inux \textbf{U}tility \textbf{R}esource \textbf{M}anager~\\ or simply known as the \emph{SLURM scheduler}
	\numlessfootnotetxt{\tiny \url{https://en.wikipedia.org/wiki/Slurm_Workload_Manager}}
	\numlessfootnotetxt{\tiny \url{http://slurm.schedmd.com/slurm.html}}
\end{frame}

>>>>

\begin{frame}
	\frametitle{What is a Job Scheduler?}
	Basic features expected of a job scheduler include:
	\begin{itemize}\footnotesize
        \item The capability to control and prioritize the execution order of unrelated jobs
        \item Allocate exclusive and/or non-exclusive access to resources to users for some duration of time so they can perform work
	\item Provides a framework for starting, executing, and monitoring work on the set of allocated resources
	\item Arbitrate contention for resources by managing a queue of pending work
	\end{itemize}
	\bigskip
	For the {\craycs}, we utilize the \textbf{S}imple \textbf{L}inux \textbf{U}tility for \textbf{R}esource \textbf{M}anager~\\ or simply known as the \emph{SLURM scheduler}
	\numlessfootnotetxt{\tiny \url{https://en.wikipedia.org/wiki/Slurm_Workload_Manager}}
	\numlessfootnotetxt{\tiny \url{http://slurm.schedmd.com/slurm.html}}
\end{frame}
